### 2016-07-08 resdisc.tex
some reordering and copyediting

%!TEX root =  autocontgrlp.tex
\section{Discussion}
The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
\begin{enumerate}
\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
\item $||\Gamma J^*-\hg J^*||_{\mn}$.
\end{enumerate}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators. As a consequence, our result holds with probability $1$, unlike prior results on constraint sampling \cite{CS} that hold only with high probability. The error term $\etmn$ gives new insights into constraint selection. 
\begin{theorem}\label{st}
Let $s\in S$ be a state whose constraint was selected. Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align}
\end{theorem}
\begin{proof}
Let $r_{e_s,J^*}$ and ${r}'_{e_s,J^*}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$. However, since the constraints with respect to state $s$ have been sampled we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
\end{proof}
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.\par
The GRLP has linear function approximation in both the primal and dual variables of the LP formulation. To understand this, we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
\end{align}
Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approxmation of the Lagrange multipliers. Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e., 
\begin{align}
\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
\end{align}
where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Discussion}
The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
\begin{enumerate}
\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
\item $||\Gamma J^*-\hg J^*||_{\mn}$.
\end{enumerate}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators. As a consequence, our result holds with probability $1$, unlike prior results on constraint sampling \cite{CS} that hold only with high probability. The error term $\etmn$ gives new insights into constraint selection. 
\begin{theorem}\label{st}
Let $s\in S$ be a state whose constraint was selected. Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align}
\end{theorem}
\begin{proof}
Let $r_{e_s,J^*}$ and ${r}'_{e_s,J^*}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$. However, since the constraints with respect to state $s$ have been sampled we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
\end{proof}
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.
